### 2024-09-05 download-football-data.qmd
20240904 - fix comment

# Seasonal Projections
players_projections_seasonal_raw <- ffanalytics::scrape_data(
  season = NULL, # NULL grabs the current season
  week = 0) # NULL grabs seasonal projections; NULL grabs the current week

>>>>

# Seasonal Projections
players_projections_seasonal_raw <- ffanalytics::scrape_data(
  season = NULL, # NULL grabs the current season
  week = 0) # 0 grabs seasonal projections
